HPC--101\\Onboarding

### 2017-02-04 hpc_101/sections/02_cluster.tex
compressed storage slides

\begin{frame}
	\frametitle{{\craycs} -- Storage}
	Two storage options are currently available on the {\craycs}
	\begin{enumerate}
		\item {\lustre}
                  \begin{itemize}
                  \item High performance parallel filesystem 
                  \item Available on all the cluster nodes
                    \item Freely available to all users
                  \end{itemize}
		\item ValueStorage
                  \begin{itemize}
                  \item Network attached scale out storage
                  \item Only available from the login nodes
                  \item Available as a for fee service
                  \end{itemize}
	\end{enumerate}
\end{frame}

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ {\lustre}}
	\begin{itemize}
		\item The {\craycs} has $\approx582$TB of storage space

		\item Primarily used as scratch space for jobs (Input and Output)
		\item User do not have a usage quota (soft or hard)
		\item Certain directories are subject to a 90 day purge policy
		\item \textbf{Data is not backed up!  Users are responsible for their own data}
                \item {\lustre} utilizes RAID 6 arrays, and is fairly robust but \ldots~\\RAID is not a backup
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ ValueStorage}
        ~\\
	\begin{itemize}
		\item $500$TB of scale out storage
		\item Purchased annually in 0.5TB increments 
	\end{itemize}
	\btVFill

	\begin{center}
	\textbf{ValueStorage Pricing}~\\ 
		\resizebox{0.50\textwidth}{!}{%
		\begin{tabular}{l r }
			\toprule
			\textbf{Product} & \textbf{Annual Cost}~~ \\
	                \midrule
			\midrule
			0.5TB & \$65.00\\
                        0.5TB + Replication  & \$130.00 \\
			\bottomrule
		\end{tabular}
		}
		~\\ \href{http://www.hawaii.edu/its/value-storage-pricing/}{More Information}
		~\\	{\footnotesize \emph{All prices are subject to change}}
	\end{center}
\end{frame}

>>>>

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ {\lustre}}
	\begin{itemize}
        \item Lustre is a high performance parallel filesystem 
        \item Available on all the cluster nodes

	\item The {\craycs} has $\approx582$TB of storage space

		\item Primarily used as scratch space for jobs (Input and Output)
		\item User do not have a usage quota (soft or hard)
		\item Certain directories are subject to a 90 day purge policy
		\item \textbf{Data is not backed up!  Users are responsible for their own data}
                \item {\lustre} utilizes RAID 6 arrays, and is fairly robust but \ldots~\\RAID is not a backup

	\end{itemize}
\end{frame}
